PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-11-19 qfenv_paper/qf_environment.tex
Minor EDP issue fixed
EDP Mr binsize reduced which caused minor adjustments in EDP. Tightened
SMF, but did nothing to QF.

Before we measure the environment for our galaxy sample, we first
construct a volume limited Environment Defining Population (EDP) with
absolute magnitude cut-offs ($M_{r}$) in redshift bins with $\Delta z
\sim 0.2$. The $M_{r}$ cut-offs for the EDP are selected such that the
cumulative number density over $M_{r}$ for all redshift bins are
equal.  We make this choice in order to construct an EDP that contains
similar galaxy populations through the redshift range (i.e. accounts
for the progenitor bias). In their analysis of this method,
\cite{Behroozi:2013aa} and \cite{Leja:2013aa} find that although it
does not precisely account for the scatter in mass accretion or
galaxy-galaxy mergers, it provides a reasonable means to compare
galaxy populations over a wide range of cosmic time.

>>>>

Before we measure the environment for our galaxy sample, we first
construct a volume limited environment defining population (EDP) with
absolute magnitude cut-offs ($M_{r}$) in redshift bins with $\Delta z
\sim 0.2$. The $M_{r}$ cut-offs for the EDP are selected such that the
cumulative number density over $M_{r}$ for all redshift bins are
equal.  We make this choice in order to construct an EDP that contains
similar galaxy populations through the redshift range (i.e. accounts
for the progenitor bias). In their analysis of this method,
\cite{Behroozi:2013aa} and \cite{Leja:2013aa} find that although it
does not precisely account for the scatter in mass accretion or
galaxy-galaxy mergers, it provides a reasonable means to compare
galaxy populations over a wide range of cosmic time.
